\documentclass[]{vishrutrao-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Vishrut K.}{Rao}{ \urlstyle{same}\url{http://vishrutrao.com} \\
\href{mailto:vishrutrao@tamu.edu}{vishrut555@tamu.edu} | 832.790.7024
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Texas A\&M University}
\descript{BS in Biology}
\location{Expected May 2018 | College Station, TX}
Minor in Computer Science and Bioinformatics \\
College of Science \\
Dean's List (All Semesters) \\
\location{ Major GPA: 3.73 / 4.0}
\sectionsep


\subsection{Cinco Ranch High School}
\location{Grad. May 2014|  Katy, Texas}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/vishrutrao}{\custombold{vishrutrao}} \\
LinkedIn://  \href{https://www.linkedin.com/in/vishrut-rao-b76907b1}{\custombold{vishrutrao}} \\
Website://  \href{https://www.vishrutrao.com/}{\custombold{vishrutrao}} \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Honors}
Molecular Biology \\
Genetics \\
\sectionsep

\subsection{Undergraduate}
Data Structures and Algorithms \\
Computer Organization \\
Introduction to Computing \\
Bioinformatics \\
Computational Genomics \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced}
Java \textbullet{}   C \textbullet{} C++ \textbullet{} Matlab \\
R \textbullet{} JavaScript \textbullet{} Python \textbullet{} \LaTeX\ \\ 
Emacs \textbullet{} HTML/CSS \\

\location{Familiar:}
Android 
\sectionsep

\subsection{Applications}
\location{Experienced}
Photoshop \textbullet{} After Effects \textbullet{} Premiere Pro \\
Lightroom 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Texas A\&M University REC Center}
\descript{| Head Attendant }
\location{ May 2016 – May 2017 | College Station, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Monitor safety for risk management purposes while maintain supplies for
up to 300+ patrons. \item Manage strength and conditioning staff to ensure excellent customer
service within the 30,000 square foot facility. \item Teach patrons safe and effective ways to use equipment and perform exercises.
\end{tightemize}
\sectionsep

\runsubsection{Laversab Inc.}
\descript{| Engineering Intern }
\location{May 2014 – Jul 2014 | Sugar Land, TX}
\begin{tightemize}
\item Filed and assigned RMA's (Return Merchandise Authorization).\item Used Excel and Word to make appropriate presentations for expenses and memos. \item Assembled Pitot Static Test Equipment which were rugged, portable, and waterproof. \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Material Science Research Lab}
\descript{| Undergrad Research}
\location{May 2017 – Present | College Station, TX}
\begin{tightemize}\item Worked with \textbf{\href{http://www.bio.tamu.edu/index.php/faculty/aramayo/}{Dr. Rodolfo Aramayo}} and \textbf{\href{https://sites.google.com/a/arroyavelab.net/wiki/}{Dr. Raymundo Arroyave}} to create \textbf{MSGalaxy}, a materials-focused extension of the widely used Galaxy scientific workflow management system (SWMS). \item I also developed tools for MSGalaxy which would speed up discovery and guarantee accessibility, reproducibility, and transparency of advanced materials discovery/development workflows. \item Publication submitted.
\end{tightemize}
\sectionsep

\runsubsection{Bacteriophysiology Lab}
\descript{| Undergrad Research}
\location{Aug 2016 – May 2017 | College Station, TX}
\begin{tightemize}\item Investigated the biochemical and physical basis of bacterial chemotaxis and motility in various E. coli strains with  \textbf{\href{https://biochemistry.tamu.edu/people/manson-michael/}{Dr. Michael Manson}.}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS AND AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects and Awards} 
\begin{tabular}{rll}
2017	     & $\textbf{Personal Website}$ \\
             & Developed my personal website to showcase projects \\
             & and my photography and cinematography hobby.\\
2017	     & Alpha Phi Omega Chapter Forget-Me-Not Award\\
             & Awarded to students who made their outstanding and unique \\
             & contribution to the chapter as a whole and exemplified the cardinal principles. \\
2015	     & College of Science Dean's List\\
             & Awarded to students who receive $\geq$ 3.75 GPA.\\
2014	     & Scholarships\\
             & 80\% of education financed through employment, grants, and scholarships. \\ 

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

Alpha Phi Omega - Service Organization\\
Century Men's Society - Men's Leadership and Service Organization \\
Freshman Leaders Advancing in Service and Honor \\

\sectionsep

\end{minipage} 
\end{document}


